\documentclass{beamer}% This is the file main.tex
\usepackage{graphicx}
\usepackage{outlines}
\usepackage{gensymb}
\usepackage{pgfplots}
\pgfplotsset{compat=1.11}
\usepackage{tikz}


\usetheme{Boadilla}
\title{Choosing Gear Ratios}
\author{Thad Hughes}
\date{\today}

\hypersetup{%
  colorlinks=false,% hyperlinks will be black
  linkbordercolor=red,% hyperlink borders will be red
  pdfborderstyle={/S/U/W 1}% border style will be underline of width 1pt
}

\begin{document}

\maketitle

\begin{frame}
\frametitle{Outline}
\framesubtitle{Where are we going today?}

\begin{outline}
	\1 Goals
	\1 The general DE and Behavior
	\1 Solving the Calculus Way
	\1 Simulating
	\1 Making practical use of solutions/simulations
\end{outline}

\begin{alertblock}{Here Be Dragons}
	This presentation contains a lot of math. It's mostly for your interest, and doesn't really reinforce the points abotu design too much, but it might be interesting to you.
\end{alertblock}

\end{frame}

\begin{frame}
	\frametitle{Goals of a Mechanism}
	\begin{itemize}
		\item Move/lift a load to a position
		\item Move/lift a load to a velocity
		\item Minimize electrical consumption
		\item Maximize precision/controllability
	\end{itemize}
\end{frame}

\begin{frame}
	\frametitle{What is motor behavior like? (Flywheel Example)}
	\framesubtitle{Building on Motor Behavior}

	\begin{equation}
		T_{motor} = T_{max} \frac{(\omega_{max}-\omega)}{\omega_{max}}
	\end{equation}	
	
	\begin{equation}
		T_{gearbox} = G T_{motor}
	\end{equation}
	
	A flywheel with torques acting on it can be modeled as:
	
	\begin{columns}
	\column{0.5\textwidth}
	\begin{tikzpicture}[x=1.0in,y=1.0in]
		\draw[ultra thick] (0,0) circle (0.1);
		\fill[black] (0,0.1)--(0,0)--(0.1,0) arc[start angle=0, end angle=90, radius=0.1]--cycle;
		\fill[black] (0,-0.1)--(0,0)--(-0.1,0) arc[start angle=180, end angle=270, radius=0.1]--cycle;
		\draw[ultra thick, teal] (0,0) circle (0.5);
		
		%\draw[ultra thick, red, ->] (0,0.6) arc[start angle=90, end angle=180, radius=0.6] node[pos=0.7,left]{$M_{resist}$};
		\draw[ultra thick, green, ->] (0,0.6) arc[start angle=90, end angle=0, radius=0.6] node[pos=0.7,right]{$T_{gbx}$};
		
		\draw[ultra thick, blue, ->] (0,0.2) arc[start angle=90, end angle=-30, radius=0.2] node[pos=0.7,right]{$I \alpha$};
	\end{tikzpicture}	
	\column{0.5\textwidth}
	\begin{equation}
		\sum M = I \alpha
	\end{equation} 
	\begin{equation}
		T_{gbx} = I \alpha_{wheel}
	\end{equation}
	
	\end{columns}
	
\end{frame}

\begin{frame}
	\frametitle{What is motor behavior like? (Continued)}
%	\framesubtitle{Building on Motor Behavior}
	\begin{equation}
		\alpha_{wheel} = \frac{d \omega_{wheel}}{dt}
	\end{equation}\begin{equation}
		\omega_{motor} = G \omega_{wheel}
	\end{equation}\begin{equation}
		G T_{max} \frac{\omega_{max} - \omega}{\omega_{max}} = \frac{I}{G} \frac{d \omega}{dt}
	\end{equation}
	
		This is a "differential equation" ($\frac{d \omega}{dt}$ and $\omega$ are in the same equation).	
	
	\begin{alertblock}{Apology}
		This math isn't too imperative to the overall point. If you prefer to just use the calculator and look at pretty plots and trends, that's alright.
		
		There be dragons (calculus) ahead.
	\end{alertblock}	
	
\end{frame}

\begin{frame}
	\frametitle{The Mathy Approach}
	
	We can solve differential equations with math!	
	\begin{equation}
		\mbox{let } B = \frac{G^2 T_{max}}{I}
	\end{equation}\begin{equation}
		\mbox{Substitute: } B\ \frac{\omega_{max} - \omega}{\omega_{max}} = \frac{d \omega}{d t}
	\end{equation}\begin{equation}
		\mbox{Separate and integrate: } \int B\ dt = \int \frac{\omega_{max}}{\omega_{max} - \omega} d \omega
	\end{equation}\begin{equation}
		\mbox{Solve integral: } B t + C = -\omega_{max}\ ln[\omega_{max} - \omega]
	\end{equation}\begin{equation}
		\mbox{Solve for $\omega$: } \omega = \omega_{max} - C\ e^{-\frac{B t}{\omega{max}}}
	\end{equation}\begin{equation}
		\mbox{Solve for C with initial condition } \omega(0) = 0 \rightarrow C = \omega_{max}
	\end{equation}\begin{equation}
		\omega = \omega_{max}\ [1 - e^{-\frac{G^2\ T_{max}\ t}{I\ \omega{max}}}]
	\end{equation}\begin{equation}
		\omega_{gbx} = \frac{\omega_{max}}{G}\ [1 - e^{-\frac{G^2\ T_{max}\ t}{I\ \omega{max}}}]
	\end{equation}
\end{frame}

\begin{frame}
	\frametitle{Plotting the Math}
	\begin{columns}
	\column{0.35\textwidth}
		\begin{block}{}
			Acceleration is the slope of the velocity curve.
		\end{block}
		
		\begin{block}{}
		Increasing the mass of the system (or decreasing power!) will decrease acceleration.
		\end{block}\begin{block}{}		
		Increasing the gear ratio of the system will increase acceleration, but decrease maximum speed.
		\end{block}
		
	\column{0.62\textwidth}
	\centering
	\begin{tikzpicture}[x=1.0in,y=1.0in]
		%\draw[gray] (0,0)--(3,0) node[pos=0.5,below,black]{Time $t$};
		%\draw[gray] (0,0)--(0,2) node[pos=0.5,above,rotate=90,black]{Ang. Velocity $\omega_{gbx}$};
		
		%\draw[red] (0,0)
		
		\begin{axis}[grid=both,
          xmax=5,ymax=1,
          xticklabel=\empty, yticklabel=\empty,
          axis lines=middle,
          restrict y to domain=-7:12,
          xlabel={Time $t$},
          ylabel={Velocity $\omega_{gbx}$}
          ]
		\addplot[blue,domain=0:5,samples=100]  {1*(1-exp(-1^2*x))} node[pos=0.8,below] {Baseline};
		\addplot[purple,domain=0:5,samples=100]  {1*(1-exp(-1^2/2*x))} node[pos=0.7,below right] {Lower $\frac{T_{max}}{I}$};
		\addplot[red,domain=0:5,samples=100]  {1/2*(1-exp(-2^2*x))} node[above left] {Higher G};
		\end{axis}
	\end{tikzpicture}
	\begin{alertblock}{Warning}
			This assumes that there is no constant load, or friction.
			This behavior is generally true, but not exactly true.
		\end{alertblock}
	\end{columns}
\end{frame}

\begin{frame}
	\frametitle{Simulating (Actually... is easier!)}
	
	Newton's Method of numerically solving differential equations:
	\begin{equation}
		\frac{d}{dt} f(t) \approx \frac{\Delta f(t)}{\Delta t}
	\end{equation}\begin{equation}
		f(t_{i+1}) = f(t_{i}) + \frac{d}{dt}[f(t_{i})]\ {\Delta t}
	\end{equation}
	
	Another way of putting it... "the next value is the current value, plus the rate of change times the timestep of the simulation"
	
	We just need to get an expression for the $\frac{d}{dt}f(t)$ we are interested in.
	
	This process is sometimes called 'discretization' since we are taking a continuous field of time $t$ and separating it into little $\Delta t$ chunks.
\end{frame}

\begin{frame}
	\frametitle{Simulating a more complex example}
	\centering
	Let's consider a flywheel with resistance $M_{resist}$ on it.	
	
	\begin{columns}
	\column{0.3\textwidth}
	\begin{tikzpicture}[x=1.0in,y=1.0in]
		\draw[ultra thick] (0,0) circle (0.1);
		\fill[black] (0,0.1)--(0,0)--(0.1,0) arc[start angle=0, end angle=90, radius=0.1]--cycle;
		\fill[black] (0,-0.1)--(0,0)--(-0.1,0) arc[start angle=180, end angle=270, radius=0.1]--cycle;
		\draw[ultra thick, teal] (0,0) circle (0.5);
		
		\draw[ultra thick, red, ->] (0,0.6) arc[start angle=90, end angle=180, radius=0.6] node[pos=0.7,left]{$M_{resist}$};
		\draw[ultra thick, green, ->] (0,0.6) arc[start angle=90, end angle=0, radius=0.6] node[pos=0.7,right]{$T_{gbx}$};
		
		\draw[ultra thick, blue, ->] (0,0.2) arc[start angle=90, end angle=-30, radius=0.2] node[pos=0.7,right]{$I \alpha$};
	\end{tikzpicture}	
	\column{0.7\textwidth}
	\begin{equation}
		\sum M = I \alpha
	\end{equation} 
	\begin{equation}
		T_{gbx} - M_{resist} = I \alpha_{wheel}
	\end{equation}\begin{equation}
		\alpha_{wheel} = \frac{d}{dt} \omega_{wheel}
	\end{equation}

	\end{columns}		
	
	\begin{equation}
		\frac{d}{dt} \omega_{wheel} = \frac{T_{gbx} - M_{resist}}{I}
	\end{equation}
	\begin{equation}
		\frac{d}{dt} \theta_{wheel} = \omega_{wheel}
	\end{equation}
	
	
	
	\begin{block}{}
		This model in equations 20 and 21 actually contains all elements that we care about, if we consider $M_{resist}$ could be a function of the gearbox velocity or other factors as well.
	\end{block}
	
\end{frame}

\begin{frame}
	\frametitle{Using Simulators}
	
	Ari Meles-Braverman (AMB) has a nice little spreadsheet that builds hugely on the work of Jon Von Neun (JVN).
	
	%https://arimb.github.io/AMB_Design_Spreadsheet/
	
	It actually takes into consideration even more than we've talked about here (like voltage drop).
\end{frame}

\end{document}